{\bf {\Large Title....}}

### 2016-07-06 ident_manu.Rnw
ident of all state variables fig added

# top sensitive and category
toplo <- tocal$cattop
sel <- which(toplo$coll < 15)
toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
pcattop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 4, shape = 21, aes(fill = Category)) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  scale_x_continuous(breaks = 1:nrow(toplo)) + 
  scale_y_continuous('Identifiability') +
  cols +
  pthm +
  theme(legend.position = 'top') + 
  ggtitle('(c) All categories equally')

@@

grid.arrange(
  pleg, 
  arrangeGrob(
    pcat,
    arrangeGrob(ptop, pcattop, ncol = 1), 
    widths = c(1, 1),
    ncol = 2
    ), 
  ncol = 1, 
  heights = c(0.05, 1),
  bottom = 'Selected', 
  left = 'Identifiability'
)

@@

<<st>>=
load(file = 'rdata/tocal_all.Rdata')

toplo <- tocal_all$top_all %>% 
  reshape2::melt(., id.var = names(.[[1]]))

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line(size = 1) + 
  geom_hline(yintercept = 15) +
  geom_label_repel(
    aes(label = Parameter), 
    label.padding = unit(0.1, "lines"),
    box.padding = unit(2, "lines"), 
    force = 2
    ) + 
  geom_point(aes(colour = Category), size = 5) +
  coord_cartesian(ylim = c(0, 25), xlim = c(0, 16)) + 
  theme_classic() + 
  facet_wrap(~L1, scales= 'free_x', ncol = 4) + 
  scale_colour_brewer(palette = 'Set1') + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'No. selected by increasing sensitivity',
    breaks=toplo$Selected
    ) + 
  theme(
    legend.position = 'top', 
    strip.text = element_text(size = 12),
    axis.line.x = element_line(size = 0.5),
    axis.line.y = element_line(size = 0.5)
    )
@

>>>>

# top sensitive and category
toplo <- tocal$cattop
sel <- which(toplo$coll < 15)
toplo <- toplo[c(sel, rev(sel)[1] + 1), ]
toplo$Category <- factor(toplo$Category, levels = cats, labels = cats)
pcattop <- ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(size = 4, shape = 21, aes(fill = Category)) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  scale_x_continuous(breaks = 1:nrow(toplo)) + 
  scale_y_continuous('Identifiability') +
  cols +
  pthm +
  theme(legend.position = 'top') + 
  guides(fill = guide_legend(nrow = 3)) +
  ggtitle('(c) All categories equally')

@@

grid.arrange(
  pcat,
  arrangeGrob(ptop, pcattop, pleg, ncol = 1, heights = c(1, 1, 0.6)), 
  widths = c(1, 1),
  ncol = 2, 
  bottom = 'Parameters selected by sensitivity', 
  left = 'Identifiability'
)

@@

<<heurist_stts, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of selecting parameters for selected state variables. Parameters are selected by decreasing sensitivity indepent of parameter categories. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability. Selection stops after $\\gamma > 15$.', fig.height = 5, fig.width = 9, echo = F, cache = TRUE, out.width = '\\textwidth'>>=
data(tocal_all)

# factor levels
cats <- c('Optics', 'Organic Matter', 'Phytoplankton', 'Temperature', 'Zooplankton')
stts_lev <- c('Chla_mg_tot', 'irradiance', 'NH4', 'NO3', 'OM1', 'OM2', 'PO4')
stts_lab <- c('Chlorophyll', 'Irradiance', 'Ammonium', 'Nitrate', 'OM1', 'OM2', 'Phosphate')

# ggplot theme
pthm <- theme_minimal() + 
  theme(
    axis.text.x = element_text(size = 6), 
    axis.line.x = element_line(),
    axis.line.y = element_line(), 
    panel.grid.minor = element_blank(), 
    panel.grid.major = element_blank()
    )

# get all parameters for each state variable where coll < 15 plus one
toplo <- tocal_all$top_all %>% 
  reshape2::melt(., id.var = names(.[[1]])) %>% 
  filter(!L1 %in% 'O2') %>% 
  mutate(
    L1 = factor(L1, levels = stts_lev, labels = stts_lab),
    Category = factor(Category, levels = cats, labels = cats)
  ) %>% 
  split(., .$L1) %>% 
  lapply(function(x){
    # browser()
    sel <- which(x$coll < 15)
    x <- x[c(sel, max(sel) + 1), ] %>% 
      na.omit
    x

  }) %>% 
  do.call('rbind', .)

ggplot(toplo, aes(x = Selected, y = coll)) + 
  geom_line() + 
  geom_point(aes(fill = Category), shape = 21, size = 4) +
  geom_hline(yintercept = 15, linetype = 'longdash', colour = 'darkgrey') + 
  geom_hline(yintercept = 10, linetype = 'dotted', colour = 'darkgrey') + 
  facet_wrap(~L1, scales= 'free', ncol = 4) + 
  scale_y_continuous('Identifiability') + 
  scale_x_continuous(
    'Parameters selected by sensitivity',
    breaks = toplo$Selected
    ) + 
  cols +
  pthm +
  theme(legend.position = c(0.9, 0.2))
@
